Using Sorghum as an outgroup to find syntenic regions in Maize: regenerating

### 2017-08-11 R/SubGenome Analysis.Rmd
Added GO Analysis segment including GOSlim_Plant filter

---
title: "Using Sorghum as an outgroup to find syntenic regions in Maize: regenerating subgenome assignments in maize"
output: html_document
params:
  fileParser: "../Perl/parseKsKnFile.pl"
  goDataFile: "../Data/GO from maizecyc.tab"
  subGenomeFile: "/home/jesse/Dropbox/deleteme/outfile_processed_byHand.tab"

  #v1 vs. v1
  synMapOutputFile: "6807_8082.CDS-CDS.lastz.tdd10.cs0.filtered.dag.all.go_D20_g10_A5.aligncoords.gcoords.ks"
  inputDataFile: "../Data/sorghum_v1_vs_maize_v1.tab"
  outputFile: "../Output/recoveredSubGenomes_sorghum_v1_vs_maize_v1.tab"
  log10_ks_cutoff: 0

  #v3.1 vs v4+rejected
  # synMapOutputFile: "31607_34889.CDS-CDS.lastz.tdd10.cs0.filtered.dag.all.go_D20_g10_A5.aligncoords.gcoords"
  # inputDataFile: "../Data/sorghum_v3.1_vs_maize_v4+rejected.tab"
  # outputFile: "../Output/recoveredSubGenomes_sorghum_v3.1_vs_maize_v4+rejected.tab"
  # log10_ks_cutoff: 0
  #-0.575
---

@@

```{r GOTerms_by_subgenome, echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.width=4, fig.height=4}
# All EV-Codes, Unique GO Terms
grid.newpage()
g <- draw.pairwise.venn(
  area1 = goAnnotations.sub1 %>% select("GO Term") %>% distinct() %>% nrow(),
  area2 = goAnnotations.sub2 %>% select("GO Term") %>% distinct() %>% nrow(),
  cross.area = intersect(goAnnotations.sub1 %>% select("GO Term"), goAnnotations.sub2 %>% select("GO Term")) %>% nrow(), 
  category = c("SubGenome 1", "SubGenome 2"), 
  lty = rep("blank", 2), 
  fill = c("light blue", "green"), 
  alpha = rep(0.5, 2), 
  cat.pos = c(0, 180), 
  scaled = FALSE,
  euler.d = FALSE, 
  sep.dist = 0.3, 
  rotation.degree = 0,
  ind = FALSE
)
grid.arrange(gTree(children=g), top="GO Term by subgenome (All EV-Codes)")

#EXP only, Unique GO Terms
grid.newpage()
g <- draw.pairwise.venn(
  area1 = goAnnotations.sub1 %>% filter(grepl("EV-EXP", EVCode)) %>% select("GO Term") %>% distinct() %>% nrow(),
  area2 = goAnnotations.sub2 %>% filter(grepl("EV-EXP", EVCode)) %>% select("GO Term") %>% distinct() %>% nrow(),
  cross.area = intersect(goAnnotations.sub1 %>% filter(grepl("EV-EXP", EVCode)) %>% select("GO Term"), 
                         goAnnotations.sub2 %>% filter(grepl("EV-EXP", EVCode)) %>% select("GO Term")
                         ) %>% nrow(), 
  category = c("SubGenome 1", "SubGenome 2"), 
  lty = rep("blank", 2), 
  fill = c("light blue", "green"), 
  alpha = rep(0.5, 2), 
  cat.pos = c(0, 180), 
  scaled = FALSE,
  euler.d = FALSE, 
  sep.dist = 0.3, 
  rotation.degree = 0,
  ind = FALSE
)
grid.arrange(gTree(children=g), top="GO Term by subgenome (EV-EXP only)")
```

@@

# All EV-Codes, all assignments
grid.newpage()
g <- draw.pairwise.venn(
  area1 = goAnnotations.sub1 %>% nrow(),
  area2 = converted %>% nrow(),
  cross.area = intersect(goAnnotations.sub1 %>% select(gene2, "GO Term") %>% distinct(), 
                         converted %>% select(gene2, "GO Term") %>% distinct()
                         ) %>% nrow(),
  category = c("SubGenome 1", "SubGenome 2"), 
  lty = rep("blank", 2), 
  fill = c("light blue", "green"), 
  alpha = rep(0.5, 2), 
  cat.pos = c(0, 180), 
  scaled = FALSE,
  euler.d = FALSE, 
  sep.dist = 0.3, 
  rotation.degree = 0,
  ind = FALSE
)
grid.arrange(gTree(children=g), top="GO Term Assignments by Subgenome\n(EV-EXP only)")

@@

>>>>

---
title: 'Using Sorghum as an outgroup to find syntenic regions in Maize: regenerating
  subgenome assignments in maize'
params:
  fileParser: ../Perl/parseKsKnFile.pl
  goDataFile: ../Data/GO from maizecyc.tab
  inputDataFile: ../Data/sorghum_v1_vs_maize_v1.tab
  log10_ks_cutoff: 0
  outputFile: ../Output/recoveredSubGenomes_sorghum_v1_vs_maize_v1.tab
  subGenomeFile: /home/jesse/Dropbox/deleteme/outfile_processed_byHand.tab
  synMapOutputFile: 6807_8082.CDS-CDS.lastz.tdd10.cs0.filtered.dag.all.go_D20_g10_A5.aligncoords.gcoords.ks
output:
  html_document: default
  pdf_document: default
---

@@

```{r GOTerms_by_subgenome, echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.width=4, fig.height=4}
# All EV-Codes, Unique GO Terms
grid.newpage()
g <- draw.pairwise.venn(
  area1 = goAnnotations.sub1 %>% select("GO Term") %>% distinct() %>% nrow(),
  area2 = goAnnotations.sub2 %>% select("GO Term") %>% distinct() %>% nrow(),
  cross.area = intersect(goAnnotations.sub1 %>% select("GO Term"), goAnnotations.sub2 %>% select("GO Term")) %>% nrow(), 
  category = c("SubGenome 1", "SubGenome 2"), 
  lty = rep("blank", 2), 
  fill = c("light blue", "green"), 
  alpha = rep(0.5, 2), 
  cat.pos = c(0, 180), 
  scaled = FALSE,
  euler.d = FALSE, 
  sep.dist = 0.3, 
  rotation.degree = 0,
  ind = FALSE
)
grid.arrange(gTree(children=g), top="GO Term by Subgenome\n(All EV-Codes)")

#EXP only, Unique GO Terms
grid.newpage()
g <- draw.pairwise.venn(
  area1 = goAnnotations.sub1 %>% filter(grepl("EV-EXP", EVCode)) %>% select("GO Term") %>% distinct() %>% nrow(),
  area2 = goAnnotations.sub2 %>% filter(grepl("EV-EXP", EVCode)) %>% select("GO Term") %>% distinct() %>% nrow(),
  cross.area = intersect(goAnnotations.sub1 %>% filter(grepl("EV-EXP", EVCode)) %>% select("GO Term"), 
                         goAnnotations.sub2 %>% filter(grepl("EV-EXP", EVCode)) %>% select("GO Term")
                         ) %>% nrow(), 
  category = c("SubGenome 1", "SubGenome 2"), 
  lty = rep("blank", 2), 
  fill = c("light blue", "green"), 
  alpha = rep(0.5, 2), 
  cat.pos = c(0, 180), 
  scaled = FALSE,
  euler.d = FALSE, 
  sep.dist = 0.3, 
  rotation.degree = 0,
  ind = FALSE
)
grid.arrange(gTree(children=g), top="GO Term by Subgenome\n(EV-EXP only)")
```

@@

# All EV-Codes, all assignments
grid.newpage()
g <- draw.pairwise.venn(
  area1 = goAnnotations.sub1 %>% nrow(),
  area2 = converted %>% nrow(),
  cross.area = intersect(goAnnotations.sub1 %>% select(gene2, "GO Term") %>% distinct(), 
                         converted %>% select(gene2, "GO Term") %>% distinct()
                         ) %>% nrow(),
  category = c("SubGenome 1", "SubGenome 2"), 
  lty = rep("blank", 2), 
  fill = c("light blue", "green"), 
  alpha = rep(0.5, 2), 
  cat.pos = c(0, 180), 
  scaled = FALSE,
  euler.d = FALSE, 
  sep.dist = 0.3, 
  rotation.degree = 0,
  ind = FALSE
)
grid.arrange(gTree(children=g), top="GO Term Assignments by Subgenome\n(All EV-Codes)")

@@

GO Terms by subgenome, only counting GO Terms that are in GOSlimPlant
```{r GOTerms_by_subgenome_goslim_import, echo=FALSE}
goSlim <- read_delim("../Data/goslim_plant.tab", "\t", escape_double = FALSE, trim_ws = TRUE)
goSlim$GOSlimTerm <- paste("|",goSlim$GOSlimTerm,"|",sep = "")
```
```{r GOTerms_by_subgenome_goslim, echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.width=4, fig.height=4}
# All EV-Codes, Unique GO Terms
grid.newpage()
g <- draw.pairwise.venn(
  area1 = goAnnotations.sub1 %>% inner_join(goSlim, by=c("GO Term" = "GOSlimTerm")) %>% select("GO Term") %>% distinct() %>% nrow(),
  area2 = goAnnotations.sub2 %>% inner_join(goSlim, by=c("GO Term" = "GOSlimTerm")) %>% select("GO Term") %>% distinct() %>% nrow(),
  cross.area = intersect(goAnnotations.sub1 %>% inner_join(goSlim, by=c("GO Term" = "GOSlimTerm")) %>% select("GO Term"), 
                         goAnnotations.sub2 %>% inner_join(goSlim, by=c("GO Term" = "GOSlimTerm")) %>% select("GO Term")) %>% 
              nrow(), 
  category = c("SubGenome 1", "SubGenome 2"), 
  lty = rep("blank", 2), 
  fill = c("light blue", "green"), 
  alpha = rep(0.5, 2), 
  cat.pos = c(0, 180), 
  scaled = FALSE,
  euler.d = FALSE, 
  sep.dist = 0.3, 
  rotation.degree = 0,
  ind = FALSE
)
grid.arrange(gTree(children=g), top="GO Term by Subgenome\n(All EV-Codes, GOSlim only)")

#EXP only, Unique GO Terms
grid.newpage()
g <- draw.pairwise.venn(
  area1 = goAnnotations.sub1 %>% inner_join(goSlim, by=c("GO Term" = "GOSlimTerm")) %>% filter(grepl("EV-EXP", EVCode)) %>% select("GO Term") %>% distinct() %>% nrow(),
  area2 = goAnnotations.sub2 %>% inner_join(goSlim, by=c("GO Term" = "GOSlimTerm")) %>% filter(grepl("EV-EXP", EVCode)) %>% select("GO Term") %>% distinct() %>% nrow(),
  cross.area = intersect(goAnnotations.sub1 %>% inner_join(goSlim, by=c("GO Term" = "GOSlimTerm"))%>% filter(grepl("EV-EXP", EVCode)) %>% select("GO Term"), 
                         goAnnotations.sub2 %>% inner_join(goSlim, by=c("GO Term" = "GOSlimTerm")) %>% filter(grepl("EV-EXP", EVCode)) %>% select("GO Term")
                         ) %>% nrow(), 
  category = c("SubGenome 1", "SubGenome 2"), 
  lty = rep("blank", 2), 
  fill = c("light blue", "green"), 
  alpha = rep(0.5, 2), 
  cat.pos = c(0, 180), 
  scaled = FALSE,
  euler.d = FALSE, 
  sep.dist = 0.3, 
  rotation.degree = 0,
  ind = FALSE
)
grid.arrange(gTree(children=g), top="GO Term by Subgenome\n(EV-EXP only, GOSlim only)")
```
